A preliminary constraint grammar for Russian

### 2015-05-04 2015-nodalida-ruscg/ruscg.tex
multicols for fig 1
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60240 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{times}
\usepackage{latexsym}
\usepackage{fixltx2e} %allows subscripts
\usepackage{tipa} %allows IPA symbols
\usepackage{linguex}
%\usepackage[multiple]{footmisc} % separates consecutive footnotes with comma
%\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\begin{figure*}
\centering
\begin{alltt}
{\small
"<\rus{В}>"                                         "<\rus{работу}>"
    "\rus{в}" pr                                        "\rus{работа}" n f nn sg acc

"<\rus{ноябре}>"                                    "<\rus{Международный}>"
    "\rus{ноябрь}" n m nn sg prp                        "\rus{международный}" adj m an sg nom
                                                 "\rus{международный}" adj m nn sg acc
"<1994>"                                        
    "1994" num                                      "<\rus{трибунал}>"
                                                        "\rus{трибунал}" n m nn sg acc
"<\rus{года}>"                                          "\rus{трибунал}" n m nn sg nom
    "\rus{год}" n m nn sg gen SELECT:r462                             
;   "\rus{год}" n m nn pl nom fac SELECT:r462       "<\rus{по}>"
                                                        "\rus{по}" pr 
"<\rus{в}>"                                                             
    "\rus{в}" pr                                    "<\rus{Руанде}>" 
                                                        "\rus{Руанда}" np al f nn sg prp 
"<\rus{Танзании}>"                                      "\rus{Руанда}" np al f nn sg dat
    "\rus{Танзания}" np al f nn pl acc                           
    "\rus{Танзания}" np al f nn sg prp              "<.>" 
;   "\rus{Танзания}" np al f nn pl nom REMOVE:r424      "." sent 
;   "\rus{Танзания}" np al f nn sg dat REMOVE:r433 
;   "\rus{Танзания}" np al f nn sg gen REMOVE:r433

"<\rus{начал}>"
    "\rus{начало}" n nt nn pl gen
    "\rus{начать}" vblex perf tv past m sg
;   "\rus{начать}" vblex perf iv past m sg REMOVE:r769
}
\end{alltt}
  \caption{Example output from the morphological analyser and constraint grammar for the sentence \rus{В ноябре 1994 
           года в Танзании начал работу Международный трибунал по Руанде.} ``The work of the International Tribunal 
           for Rwanda started in Tanzania in November 1994.'' The input ambiguity is 1.76 readings per word and 
           the output ambiguity is 1.38 readings per word. Recall is 1.0 and precision is 0.72. Figure~\ref{fig:rules} 
           shows the rules that fired for this example sentence.} 
  \label{fig:output}
\end{figure*}

>>>>

\usepackage{times}
\usepackage{latexsym}
\usepackage{fixltx2e} %allows subscripts
\usepackage{tipa} %allows IPA symbols
\usepackage{linguex}
\usepackage{multicol}
%\usepackage[multiple]{footmisc} % separates consecutive footnotes with comma
%\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\begin{figure*}
\centering
\begin{multicols}{2}
\begin{alltt}
{\small

"<\rus{В}>"
    "\rus{в}" pr

"<\rus{ноябре}>"
    "\rus{ноябрь}" n m nn sg prp

"<1994>"
    "1994" num

"<\rus{года}>"
    "\rus{год}" n m nn sg gen SELECT:r462
;   "\rus{год}" n m nn pl nom fac SELECT:r462

"<\rus{в}>"
    "\rus{в}" pr

"<\rus{Танзании}>"
    "\rus{Танзания}" np al f nn pl acc
    "\rus{Танзания}" np al f nn sg prp
;   "\rus{Танзания}" np al f nn pl nom REMOVE:r424
;   "\rus{Танзания}" np al f nn sg dat REMOVE:r433
;   "\rus{Танзания}" np al f nn sg gen REMOVE:r433

"<\rus{начал}>"
    "\rus{начало}" n nt nn pl gen
    "\rus{начать}" vblex perf tv past m sg
;   "\rus{начать}" vblex perf iv past m sg REMOVE:r769

"<\rus{работу}>"
    "\rus{работа}" n f nn sg acc

"<\rus{Международный}>"
    "\rus{международный}" adj m an sg nom
    "\rus{международный}" adj m nn sg acc

"<\rus{трибунал}>"
    "\rus{трибунал}" n m nn sg acc
    "\rus{трибунал}" n m nn sg nom

"<\rus{по}>"
    "\rus{по}" pr

"<\rus{Руанде}>"
    "\rus{Руанда}" np al f nn sg prp
    "\rus{Руанда}" np al f nn sg dat
"<.>"
    "." sent
}
\end{alltt}
\end{multicols}
  \caption{Example output from the morphological analyser and constraint grammar for the sentence \rus{В ноябре 1994 
           года в Танзании начал работу Международный трибунал по Руанде.} ``The work of the International Tribunal 
           for Rwanda started in Tanzania in November 1994.'' The input ambiguity is 1.76 readings per word and 
           the output ambiguity is 1.38 readings per word. Recall is 1.0 and precision is 0.72. Figure~\ref{fig:rules} 
           shows the rules that fired for this example sentence.} 
  \label{fig:output}
\end{figure*}
